---
title: "Electricity Market"
author: "Yunus Emre Toprak"
output: html_document
date: "24.08.2020"
---
# Packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library, echo = FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(lubridate)
```

# Introduction  

In this analysis, we are going to analyze the data of the electricity prices from 01 - 31.07.2020. You can check information from [here](https://boun-ie48a.github.io/files/electricity_markets_mini_tutorial)

# Data read

After downloading the data, we will import the data to an object called `data`. After importing the data we can observe the data with glimpse function.

```{r data}
data = read.csv("C:/Users/Yunus Emre TOPRAK/Desktop/ptf-smf1.csv")
data %>% glimpse()
```

# Adjustment

The type of the date field is string, we need to change the type of that column. 

```{r preprocessing}
data$PTF = as.numeric(gsub(",", ".", gsub("\\.", "", data$PTF)))
data$SMF = as.numeric(gsub(",", ".", gsub("\\.", "", data$SMF)))
data$Negatif.Dengesizlik.Fiyatı..TL.MWh. = as.numeric(gsub(",", ".", gsub("\\.", "", data$Negatif.Dengesizlik.Fiyatı..TL.MWh.)))
data$Pozitif.Dengesizlik.Fiyatı..TL.MWh. = as.numeric(gsub(",", ".", gsub("\\.", "", data$Pozitif.Dengesizlik.Fiyatı..TL.MWh.)))
data$Tarih = gsub(pattern = "\\.","-",data$Tarih)
data_last = data %>%
  select(Date = Tarih, MCP = PTF, SMP = SMF, NIP = Negatif.Dengesizlik.Fiyatı..TL.MWh., PIP = Pozitif.Dengesizlik.Fiyatı..TL.MWh., SMPDirection = SMF.Yön) %>%
  mutate(DateTime = as.POSIXct(factor(Date), format = "%d-%m-%y %H:%M")) %>%
  mutate(Day = wday(DateTime, week_start = 1), Hour = hour(DateTime), Date = as.Date(Date, format = "%d-%m-%y %H:%M"))
data_last %>% glimpse()
```


